\section{Containerization}
\label{sec:containerization}
% \todo{subsection of 2?}

To run TransFuser in a reproducible and stable environment,
we defined a Docker container \cite{software:docker}
that contains all required dependencies.

The containerization approach enables reliable reproducability
as well as robust deployment regardless of the target environment.
Our main motivation for this approach is the simplified deployment
required to train and evaluate TransFuser.

Note that we do not use the conda \cite{software:conda} environment
as provided by the TransFuser authors,
but instead install required packages
using the more traditional \texttt{pip} tool \cite{software:pip}.

However, the Docker container runtime is not well-suited for all environments.
Specifically, for HPC clusters such as Idun,
the Singularity container runtime \cite{software:singularity} is often preferred \cite{princeton:singularity}.
Singularity provides several benefits for HPC administrators,
such as preventing users from requiring root privileges, \todo{cite downsides of root access?}
and its immutable container images that simplify concurrent access from multiple compute nodes. \todo{cite something?}

Therefore, as preparations to utilize the Idun cluster for future experiments,
we have developed a method to run the CARLA simulator and clients on Idun.
In short, we utilize our existing experience with Docker to make
Dockerfiles as container definitions,
then convert these to Singularity images using the
\texttt{singularity build} tool.
These Singularity images can be run on Idun
both manually and in batch jobs using the Slurm workload manager.
During development,
we have tested executing batch jobs with both CARLA and a simple client we developed called Carlo.\footnote{\url{https://github.com/aasewold/carlo}}
Detailed descriptions can be found in \autoref{app:instructions}.
In short,
we provide a Slurm script capable of launching
an arbitrary number of jobs,
where each job consists of an instance of the CARLA simulator and a connected client,
for instance an expert agent, TransFuser, or a reinforcement-learning agent.
This makes it possible to perform tasks such as
dataset generation,
TransFuser training and evaluation,
and reinforcement-learning algorithms such as Direct Policy Learning which require an interactive environment,
on the Idun cluster.
