\section*{Participants}
%Researchers are the main participants of the project. 
I am a master's student in computer science and will be responsible of planning and executing the project. I need to be careful of my own confirmation bias when analyzing the results, and therefore it is helpful to work with two supervisors from the Department of Computer Science: Professor Frank Lindseth and Associate Professor Gabriel Kiss. Lindseth is the main supervisor, and he is responsible for monitoring the research project, hosting recurrent meetings and providing insights into the field of autonmous driving. Kiss is the co-supervisor, and he will provide his expertise on the topic of image processing. Both will help me ensure I stay on track and work towards answering the research questions. 

There is no need to involve non-researchers on this quantitative study based on simulation data. We should however still be aware of ethical issues regarding the deployment of autonomous vehicles, especially in adverse weather conditions. We will therefore be careful to note that our experiments were done in a simulated environment, and that they should not be reproduced in the real world without further considerations.

\begin{comment}
Can describe that it is more of a data study than a user study (analytic)

10 %
C13: Describe all participants and their roles in the research project
C14: Explain whether/why there is a need to involve non-researcher participants
C15: Discuss the ethical issues of involving non-researcher participants and how to address them
C16: Reflect on your own role as researcher in the project, and how it will impact the validity of your results
\end{comment}